My thesis

### 2020-02-04 manuscript/index/05-appendix.Rmd
add model definitions

# Parameter Configurations
```{r}
# load model parameters 
source("R/asr-parameters.R")
```

@@

ASReview takes the following parameters/arguments:

- number of training data (included/excluded)
- a model
- a query strategy
- a balance strategy (fixed)
- feature extraction

@@

Balance Strategy

@@

Query Strategy 
:   The way papers are queried to the researcher

@@

    Maximum sampling
    :  Selects the samples with the highest prediction probability.

@@

Feature Extraction Strategy
:   Feature Extraction Strategy

@@

    Third paragraph of definition x.

@@

>>>>

# Parameter Configurations
```{r}
# load model parameters 
source("R/asr-parameters.R")
source("R/packages.R")
```

@@

model: nb
query_strategy: max
balance_strategy: double
feature_extraction: tfidf
n_instances: 1
n_queries: 10
n_prior_included: 5
n_prior_excluded: 5
mode: simulate
model_param: {}
query_param: {}
feature_param: {}
balance_param: {}
abstract_only: False

@@

@@

Query Strategy 
:   Type of active learning, determining the way papers are queried to the researcher.

@@

    Maximum sampling
    :  Selects the samples with the highest prediction probability. The references who are most likely to be included are presented first.

@@

Feature Extraction Strategy
:   The way the words in the abstracts are represented in the statistical model.

@@

@@

        doc2vec
